Designing Turk Experiments for Visual Statistical Inference

### 2013-06-12 paper_turk.tex
abstarct and introduction

\documentclass{article}

%\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
\usepackage{graphicx}
\usepackage{url}

@@

@@

Human observers are needed to evaluate lineups that are used to test the significance of findings using statistical graphics. One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk). It has the facilities to design online task that could serve the purpose of evaluation of lineups. But the MTurk website is designed to recruit workers for simple and easy tasks. Even though the task of evaluating lineups is easy, the technical design of the underlying experiment may be complex and the tools available to design this from MTurk website is just too simple. In this paper we present an alternative way to conduct the survey on lineups by designing a separate web site and getting turk worker do their job from this web site. The web site is now hosted and has been in use. Multiple experiments are already done through this web site. It turns out to be a very efficient way of getting lineups being evaluated by online observers. Getting results from this web site is very convenient and secure. This paper also describes how to design MTurk experiments to evaluate lineups.

@@

There have been some advancement in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols. The power of visual statistical inference or lineup protocol is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

In visual statistical inference the test statistics is a plot of the observed data. This plot is placed randomly in a layout of plots called lineup. The rest of the plots in the lineups are generated from the model specified by the null hypothesis. The lineup is evaluated by human observer. If the observed plot is identified in the lineup, the null hypothesis is rejected.

@@

Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{majumder:2013},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}. It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.

There are some reasons a researcher needs to evaluate a lineup. One is to assess the power of the visual test. The another reason would be to make decision based on the lineup. Other reasons could be to present the results of the conventional test with visual tools such as lineup.

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{.4}{\includegraphics{turk_work_flow.pdf}}
       \caption{Amazon Mechanical Turk workflow and data collection.}
       \label{fig:turk_work_flow}
\end{figure}

\section{Experimental Design} \label{sec:exp_design}

@@

\section{Website to Run the Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.  PHP scripting language is used and embedded with HTML for designing the web site. Javascript is used for validating the input data and producing warning message.  We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey. This has allowed us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site to transfer data to our server.

@@

\section{Payment of Turk Worker} Turk workers are usually small payee workers. There several issues related to the payment of their effort. These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.

@@

\documentclass{article}
\usepackage{times}
\usepackage{natbib}
%\usepackage{multicol}
%\RequirePackage{natbib}
\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
%\usepackage[dvips]{graphics}

\graphicspath{{images/}}
\usepackage{color}
\newcommand{\blue}[1]{{\color{blue} #1}}
\newcommand{\red}[1]{{\color{red} #1}}

\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.4in}
\setlength{\textheight}{9in}
\evensidemargin \oddsidemargin

\newtheorem{thm}{Theorem}[section]
\newtheorem{dfn}{Definition}[section]
\newtheorem{cor}{Corollary}[thm]
\newtheorem{con}{Conjecture}[thm]
%\setlength{\parindent}{0in}   % for no indent

%\topmargin -0.10in   % when making pdf
%\textheight 9.15in  % when making pdf

\setlength\parindent{0pt}

% Article top matter
\title{Turk Experiments for Visual Inference}
\author{Mahbubul Majumder, Heike Hofmann, Dianne Cook\\
        Department of Statistics, Iowa State University}
%\date{\today}  %\today is replaced with the current date

It has been found that the visual test, which does not have
distributional assumptions, has the power comparable to the classical
tests [3]. To examine the power of visual statistical inference we
recruited human subjects from Amazon Mechanical Turk \cite{turk}  for
evaluating lineups[1,2]. The Turk website is designed to recruit
workers for simple and easy tasks. Even though the task of evaluating
lineups is easy, the technical design of the experiment is complex and
the tools available to design this from Turk website is just too
simple. In this paper we present how we deal with this trouble and to
conduct our experiment.

Statistical graphics play a crucial role in exploratory data analysis, model checking and diagnosis. Until recently there were no formal visual methods in place for determining statistical significance of findings. This changed, when \citet{buja:2009} conceptually introduced two protocols for formal tests of visual findings. In this paper we take this a step further by comparing the lineup protocol \citep{buja:2009} against classical statistical testing  of the significance of regression model parameters. A human subjects experiment is conducted using simulated data to provide controlled conditions. Results suggest that the lineup protocol provides results equivalent to the uniformly most powerful (UMP) test and for some scenarios yields better power than the UMP test.
\end {abstract}

%\begin{multicols}{2}
%\twocolumn

Any statistical analysis must include some statistical graphics. For exploratory data analysis, statistical graphics play an invaluable role in model checking and diagnostics. Even though we have established mathematical procedures to obtain various statistics, we need to support the results by also producing the relevant plots.

\bibliographystyle{plain}
%\bibliographystyle{asa}
\bibliography{references}

\end{documents}

Any statistical analysis must include some statistical graphics. For exploratory data analysis, statistical graphics play an invaluable role in model checking and diagnostics. Even though we have established mathematical procedures to obtain various statistics, we need to support the results by also producing the relevant plots.

The scientific foundation of graphical methods for data analysis is well established by \cite{cleveland:1984}. In recent years we have seen several major advances in statistical graphics. Modern computing systems like R and SAS ease the production of high quality statistical plots. A grammar of graphics introduced by \cite{wilkinson:1999} presents a structured way to generate specific graphics from data and define connections between disparate types of plots.  \cite{hadley:2009} has implemented a revised version of the grammar of graphics in R, in the package {\tt ggplot2}.   \blue {Graham Wills has implemented the grammar in SPSS, but I'm not sure how to cite this.}

\citet{buja:2009}, following from \cite{gelman:2004}, proposed two protocols that allow the testing of discoveries made from statistical graphics. This work represents a major advance for graphics, because it bridges the gulf between classical statistical inference procedures and exploratory data analysis.

In this paper we compare graphical inference to classical statistical inference for a set of regression type example. We also present results of a human-subject study assessing the performance of individuals on lineup plots \citep{buja:2009} for testing significance of regression parameters.

Section \ref{sec:visual_test} describes the basic ideas of visual inference, Section \ref{sec:regression} applies these ideas to the case of inference for regression analysis. In Section \ref{sec:simulation} we outline the setup for the human-subject study and  and present results.

\begin{table*}[hbtp]
\caption{Comparison of visual inference with existing inference technique}
\centering 
\begin{tabular}{llll} 
\hline
  & Mathematical Inference &  Visual Inference \\ %[0.5ex] % inserts table %heading 
\hline
  Hypothesis & $H_0: \beta=0$ vs $H_1: \beta \ne 0$& $H_0: \beta=0$ vs $H_1: \beta \ne 0$\\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

 Test statistic & $T(y)=\frac{\hat{\beta}}{se(\hat{\beta})}$ & $T(y)=$ \begin{minipage}[h]{1cm} \begin{center} \scalebox{0.45}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} \\

 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

 Null Distribution & $f_{T(y)}(t); $\begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.55}{\includegraphics{stat_mathematical_test.pdf}} \end{center} \end{minipage} & $f_{T(y)}(t); $ \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.19}{\includegraphics{test_category.pdf}} \end{center} \end{minipage} \\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
 Reject $H_0$ if & observed $T$ is extreme & observed plot is identifiable \\
\hline 
\end{tabular}
\label{tbl:compare}
\end{table*}

\section{Visual Statistical Inference} \label{sec:visual_test} 
Visual tests are non-parametric tests of the form $H_0$: the data plot is visually not distinguishable from a null plot vs $H_1$: the data plot is visually distinguishable from a plot generated consistently with $H_0$.

Power of a plot and $p$-value have been derived in Buja and Wickham as ...

for this paper, we want to place the parametric inference of a regression setting into the framework of visual testing:

This section outlines the concepts of visual inference in comparison to the procedures of classical statistical inference. Table \ref{tbl:compare} (derived from \citet{buja:2009}) gives a summarized overview of this comparison.

Let $\theta$ be a population parameter of interest, with $\theta \in \Theta$, the parameter space. 
Any null hypothesis $H_0$ then partitions the parameter space into $\Theta_0$ and $\Theta_0^c$, with $H_0: \theta \in \Theta_0$ versus $H_1: \theta \in \Theta_0^c$.

\blue{Similarly, for any test, we have a rejection region $R$ and, complementary to that, $R^c$,  that partition the space of the test statistic, which is usually a subspace of the real numbers.}
%\subsection{Visual Statistic}

For visual inference, the statistic is -- unlike in the classical hypothesis test -- not a single value, but a graphical representation of the data chosen to display the strength of the parameter of interest, $\theta$. When the alternative hypothesis is true, it is expected that the plot of the observed data, the test statistic, will have visible feature(s) consistent with $\theta \in \Theta_0^c$, and that visual artifacts will not distinguish the test statistic as different when $H_1$ is not true. We will call a plot with this property a {\it visual statistic} for $\theta$. More formally,

\blue{

\begin{dfn} \label{dfn:test}
A \textit{visual test (statistic)} $T_\theta$ is defined as the grammar \citep{wilkinson:1999} of the plot,  consisting of type and specification of aesthetics necessary for complete reproducibility.
\end{dfn}
}

\begin{dfn}\label{dfn:lplot}
A lineup plot is a layout of $m$ visual statistics, consisting of 
\begin{itemize}\itemsep-3pt
\item $m-1$ plots simulated from the model specified by $H_0$  (null plots) and 
\item the test statistic produced by plotting the observed data, possibly arising from $H_1$.
\end{itemize}
\end{dfn}

The $(m-1)$ null plots can be considered to be samples drawn from the sampling distribution of the test statistic assuming that the null hypothesis is true.
If $H_1$ is true, \blue{we expect this to be reflected as a feature in the test statistic, i.e. the plot of the data, that makes it visually distinguishable from the null plots.}
{\em If the test statistic cannot be identified} in the lineup the conclusion is to {\em not reject the null hypothesis.}  A careful visual inspection follows, and the observer is asked to point out the plot most different from the lineup.

Since the lineup plot consists of $m$ plots, the probability of choosing any one of them is $1/m$. Thus we have type-I error probability of $1/m$.

%The lineup plot can be evaluated by one or more individuals. When a single individual identifies the observed graph in the lineup plot we report a $p$-value of at most $1/m$, otherwise the $p$-value is at least $1-\frac 1m$.

 %Notice that when $N=1$, this $p$-value is $\frac1m$.

%\subsection{Power}

For two different visual test statistics of the same observed data, the one  is better, in which a specific pattern is more easily distinguishable to the observer. This should be reflected in the power of the test. We can assess power therefore both empirically based on experimental data and through theoretical considerations.

%Next, we will develop power theoretically and then relate it to the empirical results.
\blue{We will first theoretically define and  derive the power of  a visual test in the setting of a parametric hypothesis test, i.e. we assume a test  of $H_0: \theta = 0$ vs $H_1: \theta \neq 0$ for some real valued parameter vector $\theta$. In a next step we will then relate the theoretical results to our empirical findings.}

\begin{dfn} \label{dfn:power}
For a lineup of $m$ plots the power of \blue{a visual test} $T$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_T(\theta)= 
        \begin{cases} 
              \text{Type-I error}=\frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}

For any single observer, the power of a visual test has a lower limit of $\frac1m$ since the probability that an observer will randomly pick the test statistic under $H_0$ is $\frac1m$.

When $K$ individuals evaluate a lineup plot independently, the number of successful evaluations, $U \sim \text{Binom} (K,1/m)$  under $H_0$. This leads us to obtain the probability 
\begin{equation}\label{eqn:pvalue}
Pr(U \ge u)= \sum_{k \ge u}^K {{K \choose k} \left(\frac{1}{m}\right)^k\left(1-\frac 1m\right)^{(K-k)}}
\end{equation}
where $u$ is the observed number of successful evaluations. We use this probability to  define the $p$-value for visual test $T_{\theta}$ as follows:
\begin{dfn} \label{dfn:pval}
The $p$-value associated with the decision of a visual test $T_{\theta}$ is given \blue{as the probability to observe a value at least as extreme as the test statistic $u$, 
where $u$ is the number of successful evaluations of the lineup, which leads us to a $p$-value of $P(U \ge u)$ as given in eqn (\ref{eqn:pvalue}). Since $u$ is a discrete value with boundaries 0 and $K$,
 we can also re-formulate the $p$-value in terms of upper and lower boundaries:
 \begin{equation*}
 \begin{array}{rcll}
 P(U \ge u+1) \le &p\text{-value}& (\le 1), & \text{if }u < K, \text{and in particular for } u=0\\
( 0 \le) &p\text{-value}& \le P(U \ge u-1), & \text{if }u > 1, \text{and in particular for } u=K.\\ 
 \end{array}
 \end{equation*}
 }
\red{HH: Tried to re-write it to answer the question below.
Why is the $p$ value not just $Pr(U \ge u)$ ? (We need to modify this a bit with respect to the rejection region $R$, but there should not be a difference in terms of whether we reject or accept. }

    \begin{equation*}
        \begin{cases} 
              p\text{-value} \le Pr(U \ge u)    & \text{when reject $H_0$,} \\
              p\text{-value} > 1-Pr(U \ge u)  & \text{when fail to reject $H_0$}
        \end{cases}
    \end{equation*}
\end{dfn}

%\red{HH: the following paragraph needs some adjustment in terms of t and $\theta$ - could you try to take of that, Mahbub?}\\
\red{For the following paragraph, we wanted to get rid of the absolute value of $t$ and instead look at $t \in R$ and $t \in R^c$.}

Suppose $F_{|t|}(.)$ is the distribution function of an absolute value of $t$, the classical test statistic. Suppose the associated test statistic in classical test is observed as  $t_{obs}$ with $p$-value $p_D$. By definition we have

$$p_D=Pr\left(|t| \ge t_{obs} \mid H_0\right)=1-F_{|t|}(t_{obs}) \ \ \Rightarrow \ \  |t_{obs}|=F_{|t|}^{-1}(1-p_D)$$

%Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$, the classical test statistic.
%, with non-centrality parameter $\delta$. 
Then the distribution function of $p$-value $p_D$ under $H_0$ is uniform, since:  
\begin{eqnarray}\label{dist_p}
F{p_D}(p) &=& Pr(p_D \le p)=1-Pr(1-p_D \le 1-p) \nonumber \\
  &=& 1-Pr\left(F_{|t|}^{-1}(1-p_D) \le F_{|t|}^{-1}(1-p) \right) \nonumber \\
  &=& 1-Pr\left(|t_{obs}| \le F_{|t|}^{-1}(1-p)\right) \nonumber \\
  &=&%\left\{ \begin{array}{ll}
          1-F_{|t|}\left( F_{|t|}^{-1}(1-p)\right)=p \mbox{ ; under $H_0$} 
 %         1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
%       \end{array} \right.     
\end{eqnarray}

%Thus the density of $p_D$ is Uniform(0,1)  under $H_0$. As noted by \cite{Ruppert:2007}, under $H_1$ the density of $p_D$ $$f_{p_D}(p_D; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_D);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_D))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.

\blue{Similarly, we will assume that $p_{0,i}$, $i=1, ..., m-1$ are the $p$-values associated with data corresponding to the $m-1$ null plots. Since this data is generated consistently with the null hypothesis,  the $p$-values follow a standard Uniform distribution, $p_{i,0} \sim U[0,1], i= 1, ..., m-1$ (by equation \ref{dist_p}). }

Let us think of a lineup as a head-to-head comparison of the test statistic and $m-1$ null plots. 
%Let the data plot have a $p$-value of $p_D$, and the null plots $p$ values of $p_{0, i}$ with $1 \le i \le m-1$.
We know that for each comparison the probability that the data, on which the plot is based, has the smaller $p$ value is 
\begin{eqnarray*}
P(p_D < p_{0,i}) &=& 1 - P(p_{i,0} \le p_D) = 1- \int_0^1  P(p_{i,0} \le p_D \mid p_D=t) f_{p_D}(t) dt =  \\
&=& 1 - \int_0^1 F_{p_{0,i}}(t) f_{p_D}(t) dt = 1 - \int_0^1 t f_{p_D}(t) dt = 1 - E[p_D],
\end{eqnarray*}
which, in particular, is independent of $p_{0,i}$ for all $i$.

Let us make the assumption that an onlooker is able to identify  the chart corresponding to the data with the smallest $p$-value. Further we will assume that all onlookers  have the same ability in identifying the data plot.

With that, we define $X$  as the number of null plots in a lineup, for which the $p$-value $p_{0,i}$ is smaller than $p_D$.

Then $X \sim B_{m-1, E[p_D]}$, and the probability that an onlooker will pick the data plot in a given lineup is 
\[
P(X=0) = \left(1 - E[p_D] \right)^{m-1} = P(p_D \le p_0), \ \ \ \text{ where } p_0 = \min_{1 \le i \le m-1}  \ p_{0,i}.
\]

%\red{pull the results for $P(p_D < p_{i,0})$ and $P(p_D < p_0)$ to the front, including the figure on $1/m$ versus power. These results are independent of the regression setting - they don't make any assumptions in terms of regression.}

Figure \ref{fig:pval_power} gives an overview of the probability of picking the data plot for lineups of different size: as $m$ increases we have an increased probability to observe a more highly structured null plot by chance. We see that for a $p$-value $p_D$ of about 0.15 for the data plot the signal in the plot is so weak, that we cannot distinguish the data plot from null plots in a lineup of size $m=20$. \red{The following sentence should be moved back} This pattern is also seen in our experiments as shown in figure \ref{fig:pval_pcorrect}.

Even under $H_1$ we expect some observers to pick a null plot with a probability that depends on the strength of the signal in our data plot. 
Reversely, we will now make use of the number of observers who do not pick the data plot in a lineup to infer the strength of the signal in the test statistic.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.5in]{images/powerplot.pdf} 
   \caption{Comparison of probabilities to pick the data plot for different size lineups $m$ and different values for data plot strength $p_D$. The grey line shows probability of picking the data plot under $H_0$. }
   \label{fig:pval_power}
\end{figure}

Now assume that the same lineup plot is evaluated by $K$ independent observers. W.l.o.g. let the last plot be the data plot and plots 1 through $m-1$ the null plots. Let $n_i$ be the number of observers who picked plot $i$ as the plot with the structure least consistent with the null hypothesis, corresponding to random variable $N_i$.  Then  $(N_1, N_2, ..., N_m) \sim$ Mult$_{\pi_1, ..., \pi_m}$ with $\sum_i \pi_i = 1$ and $\sum_{k=1}^{m} n_k = K$. We can estimate $\pi_i$ as $\widehat{\pi_i} = n_i/K$.

For the distribution of $N_m$, %the number of times out of $K$ that observers picked the last plot to show the structure least consistent with the null hypothesis, 
we get
\[
N_m\sim \left \{ 
\begin{array}{ll}
B_{K, (1-E[p_D])^{m-1}} & \text { under } H_1\\
B_{K, 1/m} & \text { under } H_0
\end{array}
\right .
\]

By matching the expected values, we therefore get an expression for the $p$-value in the data under $H_1$  as:
\begin{equation}\label{eqn:power_estimate}
{E[p_D]} = 1- \left(\frac{E[N_m]}{K}\right)^{1/(m-1)}.
\end{equation}

\blue{Note that the right hand side of equation (\ref{eqn:power_estimate}) is independent of the parameter $\theta$, but just based on the lineup evaluation by independent observers. While this allows us to compute this value independently of the parametric setting, it also means that onlookers might pick out the data plot for a reason not related to the value of $\theta$.

%Picking out the data plot is still a measure of how different the data plot is compared to the null plots, and therefore is a test statistic of the visual test.

%This allows us to compute this value independently of the parametric setting. We therefore define the {\it signal strength} of a  visual test as the following:
%
%\begin{dfn} \label{dfn:signal}
%The {\it signal strength} $\sigma_T$ of a visual test is defined as the probability to identify the data plot.
%\end{dfn}
%
%In a lineup of size $m$, evaluated by $K$ independent observers,  we can estimate the signal strength of the test as
%\[
%\sigma_T^{m-1} = \frac{n_m}{K}.
%\]
%
%In a parametric setting, signal strength of a test coincides with the power of the test.
}

\red{We need to comment on how this ties in to the rest of the paper: this is a theoretical consideration based on the assumption that observers are able to spot the plot with the smallest/a small $p$-value. $p$ value of data plot and $p$ values from null are negatively correlated (if one is low, the other has to be higher. We need to address this.}
\red{HH: should we re-run some of the lineups with different null plots?}

\blue{
\paragraph{Subject-specific power}
Probability to reject null hypothesis is power. This is intricately related to the probability to identify the data plot from the lineup. We need to address the problematic of individual specific abilities in identifying the data plot
}. 
\red{HH: need to cite some literature from cognitive science here}

\blue{Let $X_{j\ell} \sim B_{1, \pi_{j\ell}}$ be the random variable, with $X_{j\ell}= 1$, if  subject $j$ correctly identifies the data plot from lineup $\ell$, and 0 otherwise.
We can model $\pi_{j\ell}$ with a logistic regression with subject specific random effects as:
\[
\text{logit } \pi_{j\ell} = X_\ell \beta + Z u_j,  
\]
where $X_\ell$ is a matrix of fixed effects with parameter vector $\beta$ corresponding to lineup $\ell$ and $u \sim MVN(0, \sigma_u I)$  is a vector of random variables $j = 1, ..., N_\ell$ for each of $N_\ell$ subjects presented with lineup $\ell$.
}

Theoretical power for the regression parameters is derived in the next section.
\section{Inference for a Regression Model} \label{sec:regression}

Consider a linear regression model 
\begin{equation}\label{multi} Y_i = \beta_0 + \beta_1 X_{i1} + \beta_1 X_{i2} + \beta_3 X_{i1}X_{i2} + ... + \epsilon_i 
\end{equation}
where $\epsilon_i \stackrel{iid}{ \sim } N(0,\sigma^2)$, $i=1,2, .., n$. The covariates ($X_j, j=1,..,p$) can be continuous or discrete.

Suppose $X_k$ is a categorical variable with two levels, and we test the hypothesis $H_0:\beta_k=0$ vs $H_1: \beta_k \ne 0$. If the responses for the two levels of the categorical variable $X_k$ in the model are significantly different and we fit the null model to the observed data, the resulting residual plot shows two groups of residuals. To test this we generate side-by-side boxplots of the residuals conditioned on the two levels of $X_k$, as the test statistic. If $\beta_k\ne 0$ the boxplots show a vertical displacement.

In a regression setting, there is a multitude of established graphics that help with the evaluation and diagnostics of a model \citep{cook:99}. Table \ref{tbl:stat_multiple} shows an overview of some commonly used charts and their corresponding hypothesis tests. Note that some charts can be associated with several different testing situations. In our paper, we pick the examples for situation 2 and 3 as candidates.

A lineup including the test statistic  for a binary $X_k$ is shown in Figure \ref{fig:test_category}. The 19 null plots are generated  by simulating residuals from $N(0,\hat{\sigma}^2)$. The test statistic, the plot containing the observed data, is randomly placed among these null plots. If the test statistic is identifiable the null hypothesis is rejected. % with a $p$-value of at most 0.05.

\begin{figure}[hbt]
%\begin{figurehere}
   \centering
       \scalebox{0.95}{\includegraphics{test_category.pdf}}
       \caption{Lineup plot ($m=20$) for testing $H_0: \beta_k=0$. When the alternative hypothesis is true the plot of the observed data should show a vertical displacement between box plots. Which plot has the biggest vertical displacement between the boxplots?}
       \label{fig:test_category}
\end{figure}
%\end{figurehere}

\begin{table*}[hbtp] 
\caption{Test Statistics for Testing Hypothesis Related to Model $Y_i = \beta_0 + \beta_1 X_{i1} + \beta_1 X_{i2} + \beta_3 X_{i1}X_{i2} + ... + \epsilon_i  $ } 
\centering 
\begin{tabular}{m{0.5cm}m{3cm}m{2.5cm}m{2.6cm}m{5.5cm}} 
\hline\hline 
Case & Null Hypothesis & Statistic & Test Statistic & Description \\ [0.5ex] % inserts table %heading 
\hline 
1 & $H_0: \beta_0=0$ & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot with least square line overlaid. For lineup plot, we simulate data from fitted null model. \\ 
2 & $H_0: \beta_k=0$ & Residual plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_bet_p.pdf}} \end{center} \end{minipage} & Residual vs $X_k$ plots. For lineup plot, we simulate data from normal with mean 0 variance $\hat{\sigma}^2$. \\ 
3 & $H_0: \beta_k=0$ (for categorical $X_k$) & Box plots of residuals & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.45}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} & Box plot of residuals grouped by category of $X_k$. For lineup plot, we simulate data from normal with mean 0 variance $\hat{\sigma}^2$. \\
4 & $H_0: \beta_k=0$ (interaction with categorical $X_k$) & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.11}{\includegraphics{stat_interection.pdf}} \end{center} \end{minipage} & Scatter plot with least square lines of each category overlaid. For lineup plot, we simulate data from fitted null model.\\[1ex] % [1ex] adds vertical space 
5 & $H_0: X$ Linear & Residual Plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_nonlinear.pdf}} \end{center} \end{minipage} & Residual vs predictor plots with loess smoother overlaid. For lineup plot, we simulate residual data from normal with mean 0 variance $\hat{\sigma}^2$. \\ 
6 & $H_0: \sigma^2=\sigma^2_0$ & Box plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.15}{\includegraphics{stat_sigma_box.pdf}} \end{center} \end{minipage} & Box plot of standardized residual divided by  $\sigma^2_0$. For lineup plot, we simulate data from standard normal. \\ 				
7 & $H_0: \rho_{X,Y|Z}=\rho$ & Scatter Plot & \begin{minipage}[t]{2cm}\begin{center}  	\scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot of Residuals obtained by fitting partial regression. For lineup plot, we simulate data (mean 0 and variance 1) with specific correlation $\rho$. \\ 
8 & $H_0:$ Model Fits & Histogram & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.1}{\includegraphics{stat_goodness_simple.pdf}} \end{center} \end{minipage} & Histogram of the response data. For lineup plot, we simulate data from fitted model. \\[1ex] % [1ex] adds vertical space 
9 & Special case $p=1$ $H_0: \rho_{X,Y} =\rho$ & Scatter plot & \begin{minipage}[t]{2cm}\begin{center}  \scalebox{0.1}{\includegraphics{stat_intercept.pdf}} \end{center} \end{minipage} & Scatter plot with least square line overlaid For lineup plot, we simulate data with correlation $\rho$.\\			
\hline 
\end{tabular} 
\label{tbl:stat_multiple} 
\end{table*}

%\subsection{Expected power}

>>>>

\documentclass[11pt]{article}

%\usepackage{amsmath, amssymb, fullpage, amsthm, array, algorithm2e,graphicx}
\usepackage{graphicx}
\usepackage{url}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}

@@

\tableofcontents

@@

Human observers are needed to evaluate lineups that are used to test the significance of findings using statistical graphics. One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk). It has the facilities to create online task that would allow people to evaluate lineups and get paid. MTurk is designed for simple and easy tasks. The technical design of the underlying experiment for visual inference may be complex and the tools available to design this from MTurk is just too simple. In this paper we present an alternative way to conduct the survey on lineups by designing a separate web application and getting turk worker do their job from this web site. The web site is now hosted and has been in use and multiple experiments were already done. It turns out to be a very efficient way of getting lineups evaluated by online observers. Getting results from this web site is very convenient and secure. This paper also describes how to design MTurk experiments.

@@

There have been some advancements in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols. In visual statistical inference the test statistics is a plot of the observed data. This plot is placed randomly in a layout of plots called lineup. The rest of the plots in the lineups are generated from the model specified by the null hypothesis. A human observer is then asked to evaluate the lineup. If the observer detects the actual plot in the lineup, the null hypothesis is rejected.

The power of visual test is studied by Majumder \cite{majumder:2013} and it is revealed that power could be as good as conventional test and some times even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer. There are some reasons a researcher needs to evaluate lineups. One is to assess the power of the visual test \cite{heike:2012} for different visual test statistics. The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \cite{niladri:2012}. Other reasons could be to present the results of the conventional test with visual tools such as lineup.

@@

The power of visual test can be obtained theoretically \cite{majumder:2013} under some conditions. In general it is hard to obtain explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}. It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.

@@

\begin{figure}[htbp]
   \centering
       \scalebox{.4}{\includegraphics{turk_work_flow.pdf}}
       \caption{Amazon Mechanical Turk workflow and data collection.}
       \label{fig:turk_work_flow}
\end{figure}

\section{Experimental Design} \label{sec:turk_exp}

@@

\section{Web Application for Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.  PHP scripting language is used and embedded with HTML for designing the web site. Javascript is used for validating the input data and producing warning message.  We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey. This has allowed us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site to transfer data to our server.

@@

\section{Managing Turk Task} Turk workers are usually small payee workers. There several issues related to the payment of their effort. These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.

@@
